Variation on a Variational Principle

### 2020-09-14 draft1.tex
some progress; the deformation of theta's is lengthy to describe...

\newcommand{\thmref}[1]{Theorem \ref{#1}}
\newcommand{\prpref}[1]{Proposition \ref{#1}}

@@

\newcommand{\del}{\partial}
\newcommand{\ddd}[1]{{\frac{\del}{\del #1}}}
\newcommand{\vphi}{\varphi}
\newcommand{\llong}{{\text{long}}}
\newcommand{\Span}{{\text{span}}}
\newcommand{\Pol}{{\text{Pol}}}
\newcommand{\toruscomp}[1]{{\torus \times I - #1}}

@@

\begin{lemma}
Suppose we have the graph of a torihedron.
Given a non-singular extended circle pattern $c \in \CCC$ on the graph,
there exists a decomposition of the torihedron
into base-angled ideal pyramids (TODO make sure it's been defined) so that
	\begin{itemize}
		\item each interior edge of the torihedron has dihedral angles sum to $2\pi$;
		\item each boundary edge $e$ of the torihedron has dihedral angles sum to
			$\pi - \theta_e$.
	\end{itemize}
\end{lemma}

@@

\begin{define}
We say an augmentation is \emph{right-augmented} when both strands are (locally) oriented such that they cross the augmentation disk in the same direction, the crossing is positive/a right-handed half-twist. See Figure \ref{TODO}
We say an augmentation is \emph{left-augmented} if it is not right-augmented.
\end{define}

\begin{define}
Given a face $f$ of the original link diagram the \emph{augmentation sequence}
of $f$, denoted $\sigma_f$, is a cyclical sequence of symbols $0, L, R$ indexed
by vertices of $f$ going counter-clockwise, where, for $v \in \partial f$, the
$v$-th element is
\[
\sigma_f^v = 
\begin{cases}
0 \text{ if $v$ is not augmented} \\
L \text{ if $v$ is left-augmented} \\
R \text{ if $v$ is right-augmented}
\end{cases}
\]
\end{define}

@@

\begin{theorem}
Let $K$ be a weakly prime, alternating link with diagram $D$ with no bigons. Let
$L$ be a link obtained from augmenting $K$ such that there exist no sequence of
augmentations where a Left augmentation is adjacent to a Right augmentation.
Then $L$ is hyperbolic.
\end{theorem}

@@

We can think of a bow-tie in $\Gamma_T(L)$ as ``thickened edges" in the
following sense: consider the bow-tie at a crossing $v$,
and let the edges $e,e'$ of $\Gamma$ at $v$
be associated to the over-strand of $K$.
There is a cellular map from each triangle of the bow-tie
on to $e, e'$ that identifies the $\pi/2$- and 0-labelled edges,
and collapses the $\pi$-labelled edges onto $v$
(TODO see same figure).
It is not hard to see that this map extends to a cellular map
$\Psi: \Gamma_T(L) \to \Gamma$,
and in fact extends to the faces as well.
A similar story applies to $\Gamma_B$.

@@

It can be easily checked that $c$ satisfies the conditions of
\prpref{p:nghd_lift}.

with the same procedure for $\Gamma_B(L)$.

>>>>

\newcommand{\thmref}[1]{Theorem \ref{#1}}
\newcommand{\prpref}[1]{Proposition \ref{#1}}
\newcommand{\lemref}[1]{Lemma \ref{#1}}
\newcommand{\comment}[1]{}

@@

\newcommand{\del}{\partial}
\newcommand{\ddd}[1]{{\frac{\del}{\del #1}}}
\newcommand{\vphi}{\varphi}
\newcommand{\veps}{\varepsilon}
\newcommand{\llong}{{\text{long}}}
\newcommand{\Span}{{\text{span}}}
\newcommand{\Pol}{{\text{Pol}}}
\newcommand{\toruscomp}[1]{{\torus \times I - #1}}

@@

\begin{lemma}
\label{l:circpattern_polyhedra}
Suppose we have the graph of a torihedron.
Given a non-singular extended circle pattern $c \in \CCC$ on the graph,
such that all $\vphi_{\vec{e}} \in (0,\pi)$,
there exists a decomposition of the torihedron
into base-angled ideal pyramids (TODO make sure it's been defined) such that
	\begin{itemize}
		\item each interior edge of the torihedron has dihedral angles sum to $2\pi$;
		\item each boundary edge $e$ of the torihedron has dihedral angles sum to
			$\pi - \theta_e$.
	\end{itemize}
\end{lemma}

@@

\begin{define}
We say an augmentation is \emph{right-augmented} if, when both strands are
(locally) oriented such that they cross the augmentation disk in the same
direction, the crossing is positive/a right-handed half-twist. See Figure
\ref{TODO}
We say an augmentation is \emph{left-augmented} if it is not right-augmented.
\end{define}

We can recover $L$ from the link diagram of $K$
together with labels at vertices indicating left- or right-augmentation.

\comment{
\begin{define}
Given a face $f$ of the original link diagram the \emph{augmentation sequence}
of $f$, denoted $\sigma_f$, is a cyclical sequence of symbols $0, L, R$ indexed
by vertices of $f$ going counter-clockwise, where, for $v \in \partial f$, the
$v$-th element is
\[
\sigma_f^v = 
\begin{cases}
0 \text{ if $v$ is not augmented} \\
L \text{ if $v$ is left-augmented} \\
R \text{ if $v$ is right-augmented}
\end{cases}
\]
\end{define}
}

\comment{

@@

\begin{prop}
Let $\Sigma$ be a closed surface with a cellular decomposition.
Suppose we have labelled some edges by either $`+'$ or $`-'$,
such that for each face $f$,
\begin{itemize}
	\item no two adjacent edges have the same label,
	\item the length of consecutive labelled edges is at least 2.
\end{itemize}
Then one can further decompose faces along new edges,
and extend the labelling of edges,
such that every vertex is adjacent to the same number of
$`+'$'s and $`-'$'s.
\end{prop}

\begin{proof}
Consider a face $f$ and consider a maximal contiguous sequence
of labelled edges, $e_1,\ldots,e_k$ in $\del f$.
they span the vertices $v_0,\ldots,v_k$.
Suppose $e_1$ is labelled $`+'$ (the other case is similar).
Then $e_2$ is labelled $`-'$, $e_3$ is $`+'$, and so on.
\end{proof}

\textbf{Case 1}: $k$ is odd. Then we cut $f$ along a new edge
$\overline{v_0 v_k}$, and label this edge by $`-'$.

\textbf{Case 2}: $k = 2$ and . Then we cut $f$ along a new edge
\end{proof}
}

%\begin{theorem}
%Let $K$ be a weakly prime, alternating link with diagram $D$ with no bigons. Let
%$L$ be a link obtained from augmenting $K$ such that there exist no sequence of
%augmentations where a Left augmentation is adjacent to a Right augmentation.
%Then $L$ is hyperbolic.
%\end{theorem}
\begin{theorem}
Let $K$ be a weakly prime, alternating link whose diagram has no bigons.
Let $L$ be a link obtained from augmenting $K$ such that
no edge spans left- and right-augmented vertices.
Then $L$ is hyperbolic.
\end{theorem}

@@

(Hmmm... might be misleading, I think $\Psi$ should be a cellular map
$\Gamma_T(L) \to \Gamma_T(K)$, but the latter happens to be
same as $\Gamma$, so that's why it's confusing!)
We can think of a bow-tie in $\Gamma_T(L)$ as ``thickened edges" in the
following sense: consider the bow-tie at a crossing $v$,
and let the edges $e,e'$ of $\Gamma$ at $v$
be associated to the over-strand of $K$.
There is a cellular map from each triangle of the bow-tie
on to $e, e'$ that identifies the $\pi/2$- and 0-labelled edges,
and collapses the $\pi$-labelled edges onto $v$
(TODO see same figure).
It is not hard to see that this map extends to a cellular map
$\Psi: \Gamma_T(L) \to \Gamma$,
and in fact extends to the faces as well.
A similar story applies to $\Gamma_B$.

@@

It can be easily checked that $c$ satisfies the conditions of
\prpref{p:nghd_lift}.
We would like to apply \lemref{l:circpattern_polyhedra}
to obtain a polyhedral decomposition of the torihedra,
but there are edges with $\vphi_{\vec{e}}$
(specifically, those with $\theta_e = \pi$).
%We want a deformation of $\theta_{\bullet}$ of $c$
%that remains vertex non-singular,
%and gives us an honest ?? circle pattern.
Hence, we want to find a vector $a = \sum a^e \ddd{\theta_e}$
in the tangent space of $\Theta(c)$
that maintains vertex non-singularity,
i.e.  such that $\sum_{e \ni v} a^e = 0$ for all vertices $v$,
and for edges $e$ with $\theta_e = \pi$,
we have $a^e < 0$.
By \prpref{p:nghd_lift}, there exists $\veps > 0$
such that the path $\gamma(t) = \Theta(c) + t \cdot a$, $t\in [0,\veps]$,
in $\TTT$ can be lifted to a path $\tilde{\gamma}$ in $\CCC$.

To find such $a$, we need to modify $\Gamma_T(L)$ by
cutting faces along new edges.
Consider a face $f$ that is not in a bow-tie.
Suppose the corresponding face $\bar{f}$ of $\Gamma$
had vertices $v_1,\ldots,v_n$ in counter-clockwise order.
Suppose it is the case that if a vertex $v_i$ is left-augmented,
then the augmentation circle intersects $\bar{f}$
(everything is similar if it is right-augmented circles that intersect
$\bar{f}$).
Vertex $v_i$ corresponds to one edge $e_i$ of $\Gamma_T(L)$
if $v_i$ is not augmented or right-augmented,
and corresponds to two edges $e_{i,0}, e_{i,\pi}$
of $\Gamma_T(L)$ if $v_i$ is left-augmented
($e_{i,0}, e_{i,\pi}$ are edges of a single bow-tie,
and $e_{i,0}$ has $\theta_{e_{i,0}} = 0$
and $e_{i,\pi}$ has $\theta_{e_{i,\pi}} = \pi$).

Suppose, after cyclically reindexing, $v_1,\ldots,v_k$
is a maximally contiguous subsequence of left-augmented vertices
of $G(K)$ around the face $\bar{f}$;
the edges around $f$ would start
$e_{1,0}, e_{1,\pi}, e_{2,0}, e_{2,\pi}, \ldots$.
We add new edges across $f$ as follows.

First suppose $k=n$; then we do nothing.

Next suppose there is only one such maximal contiguous subsequence.
If $k = 1$, we add an edge that goes across
$e_{1,0},e_{1,\pi},e_2$
(in the sense that the new edge separates the edges of $f$ into two sets
one of them being those three edges;
since $n\geq 3$, this edge is new).
If $k = 2$, we add edge across $e_{1,0},e_{1,\pi}$
and another edge across $e_{2,0},e_{2,\pi}$
(these two edges do not form a bigon because we've ruled out $k=n$).
If $k \geq 3$,
we add an edge across $e_{1,0},e_{1,\pi},e_{2,0}$
and another edge across $e_{2,\pi},e_{3,0},\ldots,e_{k,\pi}$
(again these two edges do not form a bigon).

Finally, if there are multiple such maximal contiguous subsequences,
we just add edges as above for each contiguous subsequence.
The only caveat is that if the procedure calls to add a new edge
that would form a bigon with the existing edges,
we just don't add it.

TODO CONTINUE HERE do the $+$ and $-$ on the edges.
